systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2006-02-19 paper/trunk/systemfit.tex
considerably revised and extended "Usage" section
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@594 591db2bd-e0a0-4d22-8c19-2192dbb7da31
changed position of sections "Usaging Systemfit" and "Other Issues"
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@596 591db2bd-e0a0-4d22-8c19-2192dbb7da31
substituted "covariance matrix" for "variance-covariance matrix" and "\Cov [ . ]" for "Var [ . ]", where "\Cov" is a command for "\text{Cov}"
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@605 591db2bd-e0a0-4d22-8c19-2192dbb7da31
added package "thumbpdf" to cre

\documentclass[article]{jss}
\usepackage{csquotes}
\MakeOuterQuote{°}

@@

@@

%% an abstract and keywords
\Abstract{

  Many statistical analyses are based on models containing systems of
  structurally related equations. If the cross-equation disturbances
  are correlated, full information methods are required
  \citep{zellner62}. If exogenous variables are stochastically
  dependent on the disturbances in the system
  \citep{zellner62b,theil71}, limited information methods should be
  used for parameter estimation. The package \pkg{systemfit} provides
  the capability to estimate systems of linear and non-linear
  structural equations for limited (ordinary least squares (OLS), two
  stage-least squares (2SLS)) and full-information
  (seemingly-unrelated regression (SUR) and three-stage least squares
  (3SLS)) methods within the \proglang{R} programming environment.}

\Keywords{R, simultaneous equations estimation, ordinary least
  squares, seemingly unrelated regression, two-stage least squares,
  three-stage least squares}

@@

\input{systemfit_intro.tex}
\input{systemfit_estimation.tex}
\input{systemfit_restrictions.tex}
\input{systemfit_usage.tex}
\input{systemfit_other.tex}
\input{systemfit_summary.tex}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{systemfit} % a subset of my big bibtex file
%\bibliography{/home/suapm095/Documents/Literatur/arne}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\documentclass[article]{jss}
\usepackage[pdftex]{thumbpdf}
%   run: pdflatex *.tex -> thumbpdf *.tex -> pdflatex *.tex
\usepackage{csquotes}
\MakeOuterQuote{°}
\usepackage{amsmath}
\usepackage{float}

@@

\newcommand{\Cov}{\text{Cov}}
\clubpenalty=10000
\widowpenalty=10000

@@

%% an abstract and keywords
\Abstract{ 
Many statistical analyses are based on models containing systems of
structurally related equations.
Since in most cases cross-equation disturbances are correlated,
full information methods are required \citep{zellner62}.
If exogenous variables are stochastically dependent
on the disturbances in the system,
instrumental variable estimations should be used for parameter estimation
\citep{zellner62b}
The package \pkg{systemfit} provides the capability
to estimate systems of linear equations
within the \proglang{R} programming environment.
}

\Keywords{R, simultaneous equations systems,
  seemingly unrelated regression, two-stage least squares,
  three-stage least squares}

@@

\input{systemfit_intro.tex}
\input{systemfit_statistics.tex}
\input{systemfit_usage.tex}
\input{systemfit_summary.tex}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\bibliography{systemfit} % a subset of my big bibtex file
\bibliography{/home/suapm095/Documents/Literatur/arne}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
